# Used-Vehicle-Price-Predictive-Model-EDA

## Objectives

Here is where the pattern discovery for the model will be generated

## Libraries

```{r}
library(dplyr)#Data Manipulation
library(ggplot2)#Data Visualizations
library(tidyr)#Data Tidying and Reshaping
library(scales)#Scale Balancing
library(ggcorrplot)
```

```{r}
All_Cars <- readr::read_csv("Merge Cars.csv")
```

### Data Information

#### Data Size & Structure

```{r}
dim(All_Cars)

str(All_Cars)
```

### Data Insight to generate

These are the following insighs we are going to generate

-   Distribution of Number of Car Owners

-   Average Selling Price by Car Owners

-   Distribution of Fuel Typef

-   Average Selling Price by Fuel Type

-   Distribution Of Price

-   Relationship between kilometer driven and selling price

    ### Distribution of Number of Previous Owners

    ```{r}
    owner_dist <- All_Cars %>% group_by(no_own)%>% summarise(owner_count = n()) %>% arrange(desc(owner_count))

    #Color
    colors <- colorRampPalette(c("#FFFF00", "#FF0000"))(nrow (owner_dist))

    barplot(owner_dist$owner_count, names.arg = 
    owner_dist$no_own, main = "Distribution of number of Previous
    Owners", xlab = "Number of Owners", ylab = "Count",
    col = colors)
    abline(h = mean(owner_dist$owner_count), lty =3, lwd=3)


    ```

### Average Selling Price by Car Owners

```{r}
owner_price <- All_Cars %>% group_by(no_own) %>% summarise(avg_price= mean (Selling_price)) %>% arrange (desc(avg_price))

#color
colors_blyl <- colorRampPalette(c("#0000FF", "#ADD8E6"))(nrow(owner_price))
options(scipen = 999)

#plot
barplot(owner_price$avg_price, names.arg = 
owner_price$no_own, main= "Distribution of Prices by Number
of Previous Owners", xlab = "Number of Owners", ylab = "Price",
col = colors_blyl, yli = c(0, max(owner_price$avg_price)* 1.1))
abline(h = mean(owner_price$avg_price), lty=3, lwd=3)
```

### Distribution of Fuel Type

```{r}
ggplot(All_Cars, aes(x= fuel_type))+
  geom_bar(fill ='lightgreen', color='black')+
  labs(title = 'Frequency of Fuel Types', x='Fuel Type', y='Count')+
  theme_bw()
```

### Average Price by Fuel Type

```{r}
fuel_price <- All_Cars %>% group_by(fuel_type) %>% summarise(
  average_price= round(mean(Selling_price),0)
) %>% arrange(desc(average_price))

ggplot(data = fuel_price, aes(x=reorder(fuel_type, -average_price), 
              y=average_price, fill=fuel_type)) +
  geom_bar(stat = 'identity', fill ='lightgreen', color='black')+
  labs(title = "Average Prices of Cars by Fuel Type", y="Average Price"
       ,x="Fuel Type")
```

### Price Distribution

```{r}
ggplot(All_Cars, aes(x = Selling_price))+
  geom_histogram(bins = 45, fill = 'lightgreen', color='black')+
  geom_vline(xintercept = mean(All_Cars$Selling_price), linetype='dashed',
    color='red', linewidth =1)+
geom_vline(xintercept = median(All_Cars$Selling_price), linetype='dashed',
     color='blue', linewidth =1)+
  labs(title = "Distribution of Selling Price", x = "Selling Price", 
       y= 'Frequency')+
  theme_bw()
```

```{r}
#Selling Price vs. Year Manufactured (by fuel Type)
ggplot(All_Cars, aes(x = Year_mfd, y =Selling_price, color = fuel_type))+
  geom_point(alpha=1.5) + #Alpha for overlapping points
  geom_hline (yintercept = c(10000000, 20000000, 30000000))
  labs(title= "Selling Price vs. Year Manufactured (by Fuel Type)", 
       x="Year Manufactured", y ="Selling Price")+
  theme_bw()
```

```{r}
ggplot(All_Cars, aes( x= km_drv, y=Selling_price))+
  geom_point(alpha = 0.5, color ='blue') + #Alpha for overlapping points
  labs(tittle ="Selling Price vs. Kilometer Driven", x= "Kilometer Driven",
       y ="Selling Price")+
  theme_bw()
```

### Heatmap

```{r}
cor_matrix <- cor(All_Cars[, c("Year_mfd", "km_drv",
        "Selling_price")])#Select numerical cols

ggcorrplot(cor_matrix, method = "square", digits =2, lab = TRUE)
```
